---
title: "Vita"
draft: false
layout: cv
output: blogdown::html_page 
---

<div class='row'>

<div class='col-md-3'>
<nav id="toc" data-toggle="toc" class="sticky-top"></nav>
</div>






 

<div class='col-md-9'>

```{css css, echo=FALSE}
table td {
  vertical-align: top !important;
}

table {
  font-variant-numeric: tabular-nums;
}

.csl-entry {
  padding-left:35px;
  text-indent:-35px;
}

.csl-entry a i, .csl-entry a{
  padding-left:0px;
  text-indent:0px;
}

p img {
  max-width:900px;
}

h1 {margin-top:20px; display:block}
h2 {margin-top:15px}
h3 {margin-top:10px}
h4 {margin-top:5px}

#curriculum-vitae h1 {
font-size: 40pt
}

#education td {padding-top: 10px}

#education tr:first-child td {padding-top: 0px}

.smalldate{
  font-size: 1rem
}

```

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
library(extrafont)
loadfonts("win", quiet = TRUE)
loadfonts(quiet = TRUE)
library(tidyverse)
knitr::opts_chunk$set(echo = F, cache = F, dev = "svg")
options(knitr.kable.NA = "")
# Set table column width
# https://github.com/rstudio/bookdown/issues/122#issuecomment-221101375
html_table_width <- function(kable_output, width, class = ""){
  width_html <- paste0(
    paste0('<col width="',
           width,
           '">'),
    collapse = "\n")
  sub("<table>",
      paste0(paste0("<table class='", class, "'>"),
             "\n",
             width_html),
      kable_output)
}

make_citation_button <- function(cites, cid, date) {
  s <- ifelse(cites > 1, "s", "")
 ifelse(is.na(cites) | cites == 0, 
        "", 
        glue::glue(
          ' <a target="_blank" title="{cites} citation{s}"  href="https://scholar.google.com/scholar?as_ylo={date}&oi=bibs&hl=en&cites={cid}"><i class="ai ai-google-scholar"></i></a>')) 
}

paste_and <- function(words, 
                      sep = ", ", 
                      and = ", & ", 
                      and2 = and) {
   k <- length(words)
   sp <- rep(sep, k)
   sp[k] <- ""
   if (k > 1) sp[k - 1] <- and
   if (k == 2) sp[1] <- and2
   paste0(words, sp, collapse = "")
}

make_authors <- function(authors) {
  map_chr(authors, function(d) mutate(d, 
                         given = str_extract_all(
                           given, 
                           "\\b[a-zA-Z]") %>% 
                           map_chr(~paste0(.x, 
                                           ".", 
                                           collapse = " ")),
                         author = paste0(family, ", ", given)) %>% 
        pull(author) %>% 
        paste_and())
  
}

make_editors <- function(editors) {
  map_chr(editors, function(d) {
    s <- ifelse(nrow(d) > 1, "s", "")
    mutate(d, 
                         given = str_extract_all(
                           given, 
                           "\\b[a-zA-Z]") %>% 
                           map_chr(~paste0(.x, 
                                           ".", 
                                           collapse = " ")),
                         editors = paste0(given, " ", family)) %>% 
        pull(editors) %>% 
        paste_and() %>% 
      paste0(., " (Ed", s, ".)")
    }
        )
  
}

make_chairs <- function(d) {
  
    if (all(is.na(d))) return(NA_character_)
    
    s <- ifelse(nrow(d) > 1, "s", "")
    
    as_tibble(d) %>% 
      mutate( 
        given = str_extract_all(
          given, 
          "\\b[a-zA-Z]") %>% 
          map_chr(~paste0(.x, 
                          ".", 
                          collapse = " ")),
        editors = paste0(given, " ", family)) %>% 
      pull(editors) %>% 
      paste_and() %>% 
      paste0(". In ", ., " (Chair", s, "), ")
    
}



na2empty <- function(s, s_additional = s) {
  ifelse(is.na(s) | s == "", "", s_additional)
}

na2emph <- function(s) {
  ifelse(is.na(s) | s == "", "", paste0("<em>", s, "</em>"))
}

na2link <- function(s, href, prefix = "", suffix = ".") {
  ifelse(is.na(href), 
         na2empty(s), 
         glue::glue('{prefix}<a target="_blank" href="{href}">{s}</a>{suffix}'))
  }

title_suffix <- function(s) {
  period <- str_detect(s, "\\.$")
  questionmark <- str_detect(s, "\\?$")
  exclamationmark <- str_detect(s, "\\!$")
  ifelse(period | questionmark | exclamationmark, "", ".")
}
```

# [Curriculum Vitae]{.smallcaps}

## W. Joel Schneider

:::{.row}

:::{.col-md-7}
**Temple University**  
College of Education & Human Development  
358 Ritter Hall  
Philadelphia, PA 19122-6091
:::

:::{.col-md-5}
**Office**: (215) 204-8093  
**Email**: [schneider\@temple.edu](mailto:W. Joel Schneider <schneider@temple.edu>?subject=Question%20from%20your%20website&body=Dear%20Dr.%20Schneider%2C%0D%0A "W. Joel Schneider<schneider@temple.edu>")  
**Web**: [Faculty Profile](https://education.temple.edu/about/faculty-staff/w-joel-schneider-tuh42402){target="_blank"}  
**Blog**: [AssessingPsyche](https://assessingpsyche.wordpress.com/){target="_blank"}
:::

:::

# Education


```{r education}
tibble(
              Year = c("1996–2003", "", "1989–1994"),
         University = c("**Texas A&M University**","", 
                       "**University of California, Berkeley**"),
            Major = c("Ph.D. in Clinical Psychology [(2003)]{.smalldate}",
                       "M.S. in Clinical Psychology [(1999)]{.smalldate}",
                      "B.S. in Psychology [(1994)]{.smalldate}"),
              Note = c("Dissertation: *The Transtheoretical Model of Change in Couples*",
                       "Thesis: *The Moderating Influence of Perceived Containment on the Relation between Child Externalizing Behaviors and Parenting Practices*",
                       "")
) %>% 
  unite(University, University, Major, Note, sep = "<br>") %>%
  mutate(University = str_remove(University, "^<br>")) %>% 
  knitr::kable(format = "html", align = "ll", escape = F, col.names = NULL) %>% 
  html_table_width(width = c("20%", "80%"), class = "align-top w-100")


```


# Academic Positions 



```{r positions}
tibble::tribble(
           ~Date,                          ~Location,                         ~Position,
  "2017–",            "**Temple University**",             "Professor [(2021–)]{.smalldate}", 
              NA,                  "Philadelphia PA",             "Associate Professor [(2017–2021)]{.smalldate}",
     "2002–2017",    "**Illinois State University**",           "Professor [(2014–2017)]{.smalldate}",
              NA,                        "Normal IL", "Associate Professor [(2010–2014)]{.smalldate}",
              NA,                                 NA, "Assistant Professor [(2004–2010)]{.smalldate}",
              NA,                                 NA,  "Full-time Lecturer [(2002–2004)]{.smalldate}",
     "2001–2002",              "**Dutchess County**",               "Psychology Intern",
              NA, "**Department of Mental Hygiene**",                                NA,
              NA,                 "Poughkeepsie, NY",                                NA
  ) %>% 
  mutate(across(.fns = ~str_replace_all(.x, "–", "&NoBreak;&ndash;&NoBreak;"))) %>% 
  knitr::kable(format = "html", align = "lll", escape = F, col.names = NULL) %>% 
  html_table_width(width = c("20%", "40%", "40%"), class = "align-top w-100")


```


# Grant Support

## Current Grant Support

#. *Virtual Charter School Performance Reviews and Support [Extension]* (PI), with Christopher McGinley, Sarah Cordes, and Beth Olanaff, $480,960, Pennsylvania Department of Education [(2022–2023)]{.smalldate}.
#. *Statistical Validation Analysis of the Functional Cattell Horn Carroll (F-CHC) Model with Measures of Intelligence* (PI), $15,000, Woodcock Institute Research Grant Award [(January 2021–July 2021)]{.smalldate}.
#. *Virtual Charter School Performance Reviews and Support* (PI), with Christopher McGinley, Sarah Cordes, Beth Olanaff, and Annemarie Hindman, $511,560, Pennsylvania Department of Education [(2020–2021)]{.smalldate}.
#. *GeometryByExample: Developing an Effective Intervention for Varied Geometry Content and Learner Characteristics* (Co-PI), with Julie Booth (PI), Kelly McGinn, Christina Barbieri, & M. Suzanne Donovan, $1,396,715, US Department of Education R305A190126 [(July 2019–June 2022)]{.smalldate}.

## Past Grant Support
#. *The Roots and Fruits of Positive School Climate: A Multilevel Examination of School Climate’s Mediating Role in the Relations Among Student Risk Factors and Student Performance Outcomes* (Co-PI), with  Laura Pendergast (PI) and Armando Estrada, $3000, Pennsylvania Department of Education [(2018–2019)]{.smalldate}.
#. *Development of the Compositator* (PI), $11,000, Woodcock-Muñoz Foundation (2008–2010)
#. *Exploring the Impact of Cognitive Abilities on Behavior Problems* (PI), $2500, Illinois State University [(2005)]{.smalldate}

```{r scholar, cache=F, warning=FALSE, message=FALSE}
library(scholar)

id <- "aojOxP4AAAAJ"
l <- get_profile(id)
d_pubs <- scholar::get_publications(id)
j <- d_pubs  %>% 
  filter(number != "") %>% 
  filter(!(journal %in% c("Handbook of educational theories", 
                          "Human Intelligence: An Introduction",
                          "Scientific American",
                          "Clinical handbook of couple therapy",
                          "WJ IV clinical use and interpretation",
                          "Best practices in school psychology V",
                          "Institute for Applied Psychometrics (IAP)",
                          "The Oxford Handbook of Child Psychological Assessment",
                          "Handbook of educational theories"
                          ))) %>% 
  pull(journal) %>% 
  unique 

d_impact <- scholar::get_impactfactor(j) %>% 
  filter(!is.na(Journal)) %>% 
  mutate(linkJournal = str_to_lower(Journal))


d_pubs_link <- d_pubs %>% 
  mutate(linkJournal = str_to_lower(journal)) %>% 
  left_join(d_impact %>% select(-Journal, -Cites), by = "linkJournal") %>% 
  select(-linkJournal) %>% 
  arrange(desc(year)) %>% 
  as_tibble() %>% 
  select(title, author, year, cites, ImpactFactor) %>% 
  unique 


ct <- get_citation_history(id) %>% 
  mutate(cumulative_citations = cumsum(cites))



```

# Publications

## Publication Indices

* [Google Scholar Citations](https://scholar.google.com/citations?user=aojOxP4AAAAJ&hl=en): `r l$total_cites`
* h-index: `r l$h_index`
* i10-index: `r l$i10_index`

```{r scholarplot, dev="svg", fig.height=7, fig.width=8, fig.cap="Google Scholar Citations of My Work", out.width="800px"}
## Plot citation trend
ggplot(ct, aes(year, cumulative_citations)) + 
  geom_step(linetype = 1, color = "gray50") + 
  geom_point(color = "gray20") +
  geom_label(aes(label = paste0("+", cites)), 
             hjust = 0.5, 
             vjust = -0.5, 
             label.size = 0, 
             label.padding = unit(0,"pt"), 
             family = "Rubik", 
             size = 4.5, 
             color = "gray30", 
             fill = "white") +
  # geom_text(aes(label = paste0("+", cites)), hjust = 0.5, vjust = -0.5, family = "Palatino Linotype", size = 4, color = "gray20") +
  scale_x_continuous("Publication Year", minor_breaks = 2000:2022) +
  scale_y_continuous("Cumulative Citation Count",expand = expansion(mult = c(0.02,0.052))) +
  theme_minimal(base_size = 16, base_family = "Rubik") +
  coord_cartesian(clip = 'off') +
  theme(plot.title.position = "plot")

```

## Books

```{r books, results='asis'}
jsonlite::read_json("../data/My Books.json", simplifyVector = T) %>% 
  as_tibble() %>% 
  mutate(issued = flatten(issued) %>% as.integer(),
         edition = ifelse(is.na(edition), "", paste0(" (",scales::ordinal(as.numeric(edition)), " ed.)"))) %>% 
  unnest(author) %>% 
  mutate(given = str_extract_all(given, "\\b[a-zA-Z]") %>% 
           map_chr(~paste0(.x, ".", 
                           collapse = " ")),
         author = paste0(family, ", ", given)) %>% 
  group_by(id) %>% 
  summarise(author = knitr::combine_words(words = author, 
                                          sep = ", ", 
                                          and = " & "),
            source = first(source),
            title = first(title),
            publisher = first(publisher),
            URL = first(URL),
            edition = first(edition),
            year = first(issued),
            note = first(note)
            ) %>% 
  mutate(pubid = str_remove(note, "pubid:")) %>% 
  left_join(d_pubs %>% select(pubid, cites, cid), by = "pubid") %>% 
  mutate(citations = make_citation_button(cites, cid, year)) %>% 
  mutate(citation = glue::glue('<div class="csl-entry">{author} ({year}). <a href="{URL}"><em>{title}</em>{edition}</a>. {publisher}.{citations}</div>')) %>% 
 arrange(-year, author) %>% 
  pull(citation) %>% 
  cat

```

## Journal Articles

```{r articles, results='asis'}
jsonlite::read_json("../data/My Articles.json", simplifyVector = T) %>% 
  as_tibble() %>% 
  rename(journal = `container-title`,
         year = issued) %>% 
  mutate(year = flatten(year) %>% map(`[[`, 1) %>% as.integer(),
         author = make_authors(author),
         title = na2link(title, 
                         href = paste0("https://doi.org/", DOI), 
                         suffix = title_suffix(title)),
         pubid = str_remove(note, "pubid:"),
         issue = na2empty(issue, paste0("(", issue, ")")),
         page = ifelse(is.na(page), "", str_replace(page, "-", "&ndash;")),
         volume = ifelse(is.na(volume), "", paste0(", ", volume))) %>% 
  left_join(d_pubs %>% select(pubid, cites, cid), by = "pubid") %>% 
  mutate(citations = make_citation_button(cites, cid, year)) %>% 
  mutate(citation = glue::glue('<div class="csl-entry">{author} ({year}). {title} <em>{journal}{volume}</em>{issue}, {page}. {citations}</div>')) %>% 
 arrange(-year, author) %>%  
  pull(citation) %>% 
  str_replace("\\. ,", ".") %>% 
  cat

```



## Chapters

```{r chapters, results='asis'}


jsonlite::read_json("../data/My Chapters.json", simplifyVector = T) %>% 
  rename(book = `container-title`,
         year = issued) %>% 
  as_tibble() %>% 
  mutate(year = flatten(year) %>% as.integer(),
         author = make_authors(author),
         editor = make_editors(editor),
         pubid = str_remove(note, "pubid:"),
         page = str_replace(page, "-", "&ndash;"),
         edition = na2empty(edition, 
                            paste0(
                              scales::ordinal(as.numeric(edition)),
                              " ed., ")),
         volume = na2empty(volume, paste0("Vol. ", volume, ", ")),
         title = na2link(title, 
                         URL, 
                         suffix = title_suffix(title))) %>%  
  left_join(d_pubs %>% select(pubid, cites, cid), by = "pubid") %>% 
  mutate(citations = make_citation_button(cites, cid, year)) %>% 
  mutate(citation = glue::glue(
    '<div class="csl-entry">{author} ({year}). {title} In {editor} <em>{book}</em> ({volume}{edition}pp. {page}). {publisher}. {citations} </div>')) %>% 
 arrange(-year, author) %>% 
  pull(citation) %>% 
  cat

```


## Test Reviews

```{r testreviews, results='asis'}


jsonlite::read_json("../data/My Testreviews.json", simplifyVector = T) %>% 
  rename(book = `container-title`,
         year = issued) %>% 
  as_tibble() %>% 
  mutate(year = flatten(year) %>% as.integer(),
         author = make_authors(author),
         editor = make_editors(editor),
         citation = glue::glue(
    '<div class="csl-entry">{author} ({year}). {title}. In {editor} <em>{book}</em>. {publisher}.</div>')) %>% 
 arrange(-year, author) %>% 
  pull(citation) %>% 
  cat
```


## Scholarly Reports

```{r reports, results='asis'}


jsonlite::read_json("../data/My Reports.json", simplifyVector = T) %>% 
    as_tibble() %>% 
  rename(year = issued) %>% 
  mutate(year = flatten(year) %>% as.integer(),
         author = make_authors(author),
         pubid = str_remove(note, "pubid:"),
         publisher = paste0(na2empty(publisher), na2empty(`collection-title`), na2empty(`container-title`)),
         title = map2(title, URL, na2link)) %>% 
  left_join(d_pubs %>% select(pubid, cites, cid), by = "pubid") %>% 
  mutate(citations = make_citation_button(cites, cid, year),
         citation = glue::glue(
    '<div class="csl-entry">{author} ({year}). <em>{title}</em> {publisher}. {citations}</div>')) %>% 
 arrange(-year, author) %>% 
  pull(citation) %>% 
  paste0(collapse = "\n") %>% 
  cat
```

## Software

```{r software, results='asis'}


jsonlite::read_json("../data/My Software.json", simplifyVector = T) %>% 
    as_tibble() %>% 
  rename(year = issued) %>% 
  mutate(year = flatten(year) %>% as.integer(),
         author = make_authors(author),
         pubid = str_remove(note, "pubid:"),
         publisher = na2empty(publisher, paste0(publisher, ".")),
         title = paste0(na2link(title, URL), ifelse(is.na(URL), ".", "")),
         archive = na2link(archive, archive, "Retrieved from ", "")) %>% 
  left_join(d_pubs %>% select(pubid, cites, cid), by = "pubid") %>% 
  mutate(citations = make_citation_button(cites, cid, year),
         citation = glue::glue(
    '<div class="csl-entry">{author} ({year}). <em>{title}</em>  &#091;Software&#093; {publisher} {archive} {citations}</div>')) %>% 
 arrange(-year, author) %>% 
  pull(citation) %>% 
  paste0(collapse = "\n") %>% 
  cat
```

# Presentations

## Lectures

```{r lectures, results='asis'}

list2date <- function(l) {
  year <- l[[1]]
  month <- l[[2]]
  day <- l[[3]]
  
  date <- lubridate::as_date(glue::glue("{year}-{month}-{day}"))
  
  format(date, format = "%Y, %B %e")
  
}


jsonlite::read_json("../data/My Talks.json", simplifyVector = T) %>% 
    as_tibble() %>% 
  mutate(date = flatten(issued) %>% map_chr(list2date),
         year = flatten(issued) %>% map(1) %>% as.integer(),
         month = flatten(issued) %>% map(2) %>% as.integer(),
         day = flatten(issued) %>% map(3) %>% as.integer(),
         author = make_authors(author),
         chair = map_chr(`container-author`, make_chairs) %>% na2empty(),
         title = na2link(title, URL,suffix = title_suffix(title)),
         URL = na2empty(URL),
         `container-title` = na2emph(`container-title`)
         ) %>% 
  mutate(title = ifelse(`container-title` == "", paste0("<em>", title, "</em>"), title)
         ) %>% 
  mutate(title = paste0(title, chair, `container-title`) %>% str_replace_all("\\.\\.", ".")) %>% 
  mutate(citation = glue::glue(
    '<div class="csl-entry">{author} ({date}). {title} [{genre}]. {event}, {`event-place`}.   {URL}</div>')) %>% 
 arrange(-year, -month, -day, author) %>% 
  pull(citation) %>% 
  paste0(collapse = "\n") %>% 
  cat

```

## Posters and Papers

```{r posters, results='asis'}
jsonlite::read_json("../data/My Posters.json", simplifyVector = T) %>% 
    as_tibble() %>% 
  mutate(date = flatten(issued) %>% map_chr(list2date),
         year = flatten(issued) %>% map(1) %>% as.integer(),
         month = flatten(issued) %>% map(2) %>% as.integer(),
         day = flatten(issued) %>% map(3) %>% as.integer(),
         author = make_authors(author),
         title = na2link(title, URL, suffix = ""),
         URL = na2empty(URL)
         ) %>% 
  mutate(citation = glue::glue(
    '<div class="csl-entry">{author} ({date}). <em>{title}</em> [{genre}]. {event}, {`event-place`}.   {URL}</div>')) %>% 
 arrange(-year, -month, -day, author) %>% 
  pull(citation) %>% 
  paste0(collapse = "\n") %>% 
  cat
```


# Teaching

## Courses

### Temple University

*	CPSY 5519—Group Counseling [(Spring 2018–2019)]{.smalldate}
*	CPSY 5694—Introduction to Assessment [(Fall 2017–2019)]{.smalldate}
*	EDUC 5101—Critical Understanding of Social Science Research [(Fall 2018)]{.smalldate}
*	EDUC 5325—Introduction to Statistics and Research [(Fall 2017)]{.smalldate}
*	EPSY 5529—Tests and Measurements [(Spring 2019–2020)]{.smalldate}
*	EPSY 8825—Advanced Data Analysis [(Spring 2020)]{.smalldate}
*	SPSY 9687/8—Seminar in School Psychology/Psychoeducational Clinic [(Fall 2019, Spring 2020–2021)]{.smalldate}


### Illinois State University

*	PSY 110—Explaining Human Behavior/Fundamentals of Psychology [(Fall 2002–2006, Spring 2003–2004, 2006–2007)]{.smalldate}
*	PSY 138—Social Science Reasoning Using Statistics/Reasoning in Psychology Using Statistics [(Spring 2004, 2008–2012, 2014; Fall 2007–2014, 2016)]{.smalldate}
*	PSY 340—Statistics for the Social Sciences [(Spring 2005)]{.smalldate}
*	PSY 432—Psychodiagnostics I: Cognitive Assessment/ Theory and Practice of Cognitive Assessment [(Fall 2004–2016)]{.smalldate}
*	PSY 436—Clinical/Counseling Practicum [(Spring 2004)]{.smalldate}
*	PSY 442—Test Theory [(Spring 2015, 2017)]{.smalldate}
*	PSY 443—Regression Analysis [(Spring 2016)]{.smalldate}
*	PSY 444—Multivariate Analysis (Fall 2015){.smalldate}
*	PSY 464—Theories and Techniques of Counseling: Adults [(Spring 2005–2012, 2014–2016)]{.smalldate}
*	PSY 480—Advanced Practicum in Dialectical Behavior Therapy Skills [(Fall 2015–2017)]{.smalldate}
*	PSY 480.31—Practicum in Dialectical Behavior Therapy Skills Training [(Fall 2014, Spring 2105–2017)]{.smalldate}
*	PSY 480.33—Seminar in Psychology: Supervision of a Dialectical Behavior Therapy Group [(Fall 2014, Spring 2105, 2017)]{.smalldate}


## Mentoring

### Doctoral Dissertation Chair

#### Temple University

*	Justin Harper
*	Stephanie Iaccarino (co-chair)

#### Illinois State University

*	C. Lee Affrunti
*	Daniel L. Gadke (co-chair)
*	Jonathan W. Stagg

### Doctoral Dissertation Committee Member

#### Temple University

*	Linda Ruan
*	Kaiyla Darmer
*	Denae Sisco
*	Kathryn DeVries
*	Tera Gibbs
*	Mariah Davis

#### Illinois State University

*	Anna C. Bodner
*	Rachelle Cantin
*	Silas Dick
*	Jennifer Engelland-Schultz
*	Katherine A. Gioia
*	Trisha Mann
*	Mandi Martinez-Dick
*	Thomas Mulderink
*	Sarah Reck
*	Alyssa A. Sondalle
*	Jennifer Wallace


### Master's Thesis Chair



#### Illinois State University

*	Meera Afzal
*	Rachelle Bauer
*	Kiera Dymit
*	Feng Ji
*	David Kasson
*	Katrin Klieme
*	Sunthud Pornprasertmanit
*	Zachary Roman
*	Kristina Taylor
*	Robin Van Herrmann
*	Melissa Zygmun

### Master's Thesis Committee Member

#### Illinois State University

*	Drew Abney
*	Katy Adler
*	Leah Barr
*	Sara Byczek
*	James Clinton
*	Amanda Fisher
*	Danielle Freund
*	Jamie Hansen
*	Melanie Hewett
*	Rebecca Hoerr
*	Poonam Joshi
*	Hayley Love
*	Nicole Moore
*	Thomas Mulderink
*	Yin Ying Ong
*	Arusha Sethi
*	Anges Strojewska
*	Kevin Wallpe
*	Ryan Willard

### Honor's Thesis Chair

#### Illinois State University

*	Donnie Johnson
*	Joshua Rohlfs
*	Lauren Swanson
*	Ellen Wing


### Independent Studies

#### Temple University

*	Justin Harper (EDUC 8404—Quantitative Analysis, Part I)
*	Michael Matta (visiting scholar from University of Milan—Bicocca)

#### Illinois State University

*	Zachary Richardson (PSY 400—Creating an R package for APA Tables)

# Service


```{r, results="asis", message=FALSE}

make_service <- function(L2, L3, data) {
  if (L2 != "") cat(paste0("\n\n## ", L2, "\n\n"))
  if (!is.na(L3)) cat(paste0("\n\n### ", L3, "\n\n"))
  
  data %>% 
  mutate(across(.fns = ~str_replace_all(.x, "–", "&NoBreak;&ndash;&NoBreak;"))) %>% 
    mutate(Date = str_replace_all(Date, "-", "&ndash;")) %>% 
  knitr::kable(format = "html", align = "lll", escape = F, col.names = NULL) %>% 
  html_table_width(width = c("20%", "80%"), class = "align-top w-100") %>% 
    cat()
  
  
}


readr::read_csv("../csv/service.csv") %>% 
  group_by(L2, L3) %>% 
  nest() %>% 
  ungroup %>% 
  mutate(L2 = ifelse(L2 == lag(L2,default = ""), "", L2)) %>% 
  pwalk(make_service)



```


## Editorial Positions

```{r}
tibble::tribble(
           ~Date,                                  ~Journal,             ~Position,
  "2019–2020", "*Journal of Psychoeducational Assessment*",    "Associate Editor",
          "2015",            "*Journal of School Psychology*", "Guest Action Editor"
  ) %>% 
  mutate(across(.fns = ~str_replace_all(.x, "–", "&NoBreak;&ndash;&NoBreak;"))) %>% 
  knitr::kable(format = "html", align = "lll", escape = F, col.names = NULL) %>% 
  html_table_width(width = c("20%", "45%", "35%"), class = "align-top w-100")


```


## Editorial Boards

```{r editorial}
tibble::tribble(
             ~Date,                                  ~Journal,             ~Position,
  "2018–",                  "*Journal of Intelligence*",      "Editorial Board",
   "2011–",            "*Journal of School Psychology*",     "Editorial Board",
   "2010–", "*Journal of Psychoeducational Assessment*",     "Editorial Board",
   "2017–",       "*Archives of Scientific Psychology*",   "Consulting Editor",
      "2009–2018",                "*Psychological Assessment*",   "Consulting Editor",
      "1997–2000",             "*Clinician's Research Digest*", "Editorial Associate"
  ) %>% 
  mutate(across(.fns = ~str_replace_all(.x, "–", "&NoBreak;&ndash;&NoBreak;"))) %>% 
  knitr::kable(format = "html", align = "lll", escape = F, col.names = NULL) %>% 
  html_table_width(width = c("20%", "45%", "35%"), class = "align-top w-100")

```


## Ad Hoc Reviewing

*	*Applied Neuropsychology*
*	*European Journal of Psychological Assessment*
*	*Frontiers in Human Neuroscience*
*	*Journal of Family Psychology*
*	*Journal of Psychoeducational Assessment*
*	*NASP Communiqué*
*	*Psychological Assessment*
*	*Psychology in the Schools*

## Professional Memberships

*	Member, American Psychological Association
*	Member, National Association of School Psychologists


</div>
</div>

