---
title: Point labels perpendicular to a curve in ggplot2
author: W. Joel Schneider
date: '2021-07-27'
slug: point-labels-perpendicular-to-a-curve-in-ggplot2
categories: []
summary: "How to place legible labels for points on a curve in ggplot2"
tags:
  - ggplot2
  - R
---

```{r setup, include=FALSE}
library(tidyverse)
library(patchwork)
knitr::opts_chunk$set(dev = "svg", fig.height = 7, fig.width = 7)
```

I would like to label points on a sine function so that the labels are always legible. In a sine wave plot in which $\theta$ ranges from 0 to 2$\pi$, $\sin(\theta)$ ranges from &minus;1 to +1. Thus, the plot's xy ratio is 

$$\text{plot ratio}= \frac{2\pi-0}{1- (-1)}=\pi$$ 

The first derivative of the sine function is the cosine function. In my plot, the slope of the tangent line at each point is 

$$
\text{tangent slope} = \text{plot ratio}\times \cos(\theta)
$$
The angle of the tangent line's slope is the arctan of the slope. I would like to place the label perpendicular to the tangent line so I will add 90 degrees (i.e., $\pi/2$ radians).

$$
\text{text angle}=\tan^{-1}(\text{tangent slope})+\pi/2
$$


Now I need a pair of functions that will convert this angle into the right values for ggplot2's `hjust` and `vjust` arguments. I have added the `angle2vjust` and `angle2hjust` functions to the [WJSmisc package](https://github.com/wjschne/WJSmisc), but I have defined them here as well:

```{r}
angle2vjust <- function(theta, multiplier = 1, as_degrees = FALSE) {
  if (as_degrees) theta <- theta * pi / 180
  (((sin(theta + pi) + 1) / 2) - 0.5) * multiplier + 0.5
}

angle2hjust <- function(theta, multiplier = 1, as_degrees = FALSE) {
  if (as_degrees) theta <- theta * pi / 180
  (((cos(theta + pi) + 1) / 2) - 0.5) * multiplier + 0.5
}
```

Now we plot the sine function with labels. I have used `geom_richtext` from the [ggtext package](https://github.com/wilkelab/ggtext) because it allows me to set a white background along with padding and margins.

```{r sine-perpendicular}
library(tidyverse)
library(ggtext)

plot_ratio <- pi

tibble(theta = seq(0, 2 * pi, length.out = 13),
            y =  sin(theta),
            tangent_slope = cos(theta) * plot_ratio,
            text_angle = atan(tangent_slope) + pi / 2) %>%
  ggplot(aes(theta, y)) +
  geom_richtext(aes(label = round(y, 2),
                    vjust = angle2vjust(text_angle),
                    hjust = angle2hjust(text_angle)),
                label.color = NA,
                label.padding = unit(1, "pt"),
                label.margin = unit(5, "pt"),
                size = 4) +
  geom_point() +
  stat_function(fun = sin) +
  scale_x_continuous(expression(theta),
                     breaks = seq(0, 2 * pi, length.out = 13),
                     minor_breaks = NULL,
                     labels = function(x) round(x * 180 / pi)) +
  scale_y_continuous(expression(sin(theta))) +
  coord_fixed(ratio = plot_ratio, clip = "off") +
  theme_minimal(base_size = 16)


```

If you do not mind turning your head to one side or the other, a somewhat easier method is to set the label's `vjust` to a negative value and rotate the labels by the angle of the tangent line:


```{r sine-sloped}
tibble(theta = seq(0, 2 * pi, length.out = 13),
            y = sin(theta),
            tangent_slope = cos(theta) * plot_ratio,
            text_angle = atan(tangent_slope)) %>%
  ggplot(aes(theta, y)) +
  geom_richtext(aes(label = round(y, 2),
                    angle = text_angle * 180 / pi),
                vjust = 0,
                label.color = NA,
                label.padding = unit(1, "pt"),
                label.margin = unit(2, "pt"),
                size = 4) +
  geom_point() +
  stat_function(fun = sin) +
  scale_x_continuous(expression(theta),
                     breaks = seq(0, 2 * pi, length.out = 13),
                     minor_breaks = NULL,
                     labels = function(x) round(x * 180 / pi)) +
  scale_y_continuous(expression(sin(theta))) +
  coord_fixed(ratio = plot_ratio, clip = "off") +
  theme_minimal(base_size = 16)
```

What if you do not know the function's first derivative? You can approximate the slope of the tangent line by comparing a function's output of each point with the output of a slightly deviated point. Here is a plot of the normal cumulative distribution function.


```{r normalcdf}
# Small change in x
dx <- .00000001
plot_ratio <- 6

tibble(x = seq(-3,3,.5),
       y = pnorm(x),
       tangent_slope = plot_ratio * (pnorm(x + dx) - y) / dx,
       text_angle = atan(tangent_slope) + pi / 2,
       degrees = text_angle * 180 / pi) %>% 
  ggplot(aes(x,y)) + 
  geom_point() +
  geom_richtext(aes(label = formatC(y, 2, format = "f"),
                    vjust = angle2vjust(text_angle),
                    hjust = angle2hjust(text_angle)),
                label.color = NA,
                label.padding = unit(1, "pt"),
                label.margin = unit(5, "pt"),
                size = 4) +
  stat_function(fun = pnorm) + 
  theme_minimal(base_size = 16) + 
  coord_fixed(ratio = plot_ratio) + 
  scale_x_continuous(expression(x), breaks = -3:3) +
  scale_y_continuous(expression(Phi(x)))
```


