---
title: Creating collapsible output with knitr chunk hooks
author: W. Joel Schneider
date: '2023-06-30'
slug: creating-collapsible-output-with-knitr-chunk-hooks
categories:
  - knitr
tags:
  - R
  - knitr hooks
draft: no
summary: "How to make the output of a knitr code chunk collapsible using knitr hooks."
---



I am writing a [(still very much unfinished) psychometrics book](https://individual-psychometrics.rbind.io/) with suggested exercises using R. I wanted to provide solutions to the questions, but I wanted to hide the answers until the reader clicks them. 

An easy way to create collapsible content is with html's `<details>` tag. For example:

````{verbatim, echo = TRUE}
Create a variable `x`, and assign it a value of 5.

<details>
  <summary>Suggested Solution</summary>

```{r}
x <- 5
```
</details>
````
Create a variable `x`, and assign it a value of 5.

<details>
  <summary>Suggested Solution</summary>

```{r}
x <- 5
```
</details>

<hr>

However, I did not want to worry about all the `<details>` every time I wrote a question. To automate this process, I used two knitr hooks: a chunk hook and an option hook. 

[Chunk hooks](https://bookdown.org/yihui/rmarkdown-cookbook/chunk-hooks.html) are for customizing the output of a chunk. 

Here I create a new chunk hook that is run before and after the chunk. When it is run before the chunk, it adds the `<details>` and `<summary>` tags. After the chunk, it closes the `<details>` tag.

```{r}




# Add the details tag before running the chunk 
# and close the tag after running the chunk.
knitr::knit_hooks$set(
  solutionsetter = function(before,options) {
  
  if (before) {
    
    "\n\n<details><summary>Suggested Solution</summary>\n\n"
    
  } else {
    
    "\n\n</details>\n\n"
    
  }
})


```

If all we needed to do was to enclose the output into a `<details>` tag, then just the `solutionsetter` hook would be needed. However, I also wanted to set `echo=TRUE` so that the output would be visible even if the default for `echo` was `FALSE`. 

[Option hooks](https://bookdown.org/yihui/rmarkdown-cookbook/option-hooks.html) are great for when you have a kind of chunk you will use often, and it requires setting many chunk options at once (e.g., a plot variant with different dimensions than your default plot has).

Here I create a new option hook called `solution`. It sets the current chunk's `echo` option to `TRUE` and also triggers the new `solutionsetter` code chunk below. The updated  `options` list needs to be returned explicitly, or the hook will not work.

```{r}
knitr::opts_hooks$set(solution = function(options) {
  options$echo <- TRUE
  options$solutionsetter <- TRUE
  return(options)
})
```


Now all need to do is to set my chunk option to `solution = TRUE` and the output will be collapsible:

````{verbatim}

Create a variable `x`, and assign it a value of 5.

```{r, solution = TRUE}
x <- 5
```
````

Create a variable `x`, and assign it a value of 5.

```{r, solution = TRUE}
x <- 5
```
<hr>

# The details package

If you want a function to enclose the output of a chunk or inline code in `<details>` tags, use the [details](https://cran.r-project.org/package=details) package by Jonathan Sidi. For example, an inline chunk like this:

```{verbatim}
`r details::details("Answer", summary = "Question")`
```

Will output like so:

`r details::details("Answer", summary = "Question")`

The package has many other uses, which are explained in the [package's vignettes](https://yonicd.github.io/details/articles/index.html).
