---
title: Making text labels the same size as axis labels in ggplot2
author: W. Joel Schneider
date: '2021-08-10'
slug: making-text-labels-the-same-size-as-axis-labels-in-ggplot2
categories: []
summary: "The geom_text and geom_label functions do not specifiy text size the same way as the rest of ggplot2 elements do. For consistent text sizes, we can apply a simple conversion."
tags:
  - ggplot2
  - R
---

As explained in [this ggplot2 vignette](https://ggplot2.tidyverse.org/articles/ggplot2-specs.html#font-size-1), the `size` parameter in `geom_text` and `geom_label` is in millimeters, and the `size` parameter in all other text elements in ggplot2 is in points.

```{r setup, include=FALSE}
library(tidyverse)
```

If I specify the `base_size` of the plot and the `size` of a label to 16, you can see that the text label is much bigger than 16. 

```{r}
library(tidyverse)
textsize <- 16
ggplot() +
  stat_function(
    fun = dnorm,
    xlim = c(-4, 4),
    geom = "area",
    alpha = .3
  ) +
  theme_minimal(base_size = textsize) +
  annotate(
    geom = "text",
    x = 0,
    y = 0,
    label = "Mean = 0",
    size = textsize,
    vjust = -.1
  )
```

If you do not mind a little trial and error, you can fiddle with the `size` parameter until you find a value that looks good to you. However, what if we want the axis text labels and the output of `geom_text` to be *exactly* the same size?

We are in luck because ggplot2 has a `.pt` constant that will help us convert point sizes to millimeters. 

```{r}
ggplot2::.pt
```

We know that, by default, axis text is .8 times as large as the `base_size` of the theme. 

Let's make a function to automate the conversion:

```{r}
ggtext_size <- function(base_size, ratio = 0.8) {
  ratio * base_size / ggplot2::.pt
}
```

Now we can make the label and axis text exactly the same size:

```{r}
ggplot() + 
  stat_function(fun = dnorm, xlim = c(-4,4), geom = "area", alpha = .3) +
  theme_minimal(base_size = textsize) + 
  annotate(
    geom = "text",
    x = 0,
    y = 0,
    label = "Mean = 0",
    size = ggtext_size(textsize),
    vjust = -.3
  )
```

For my own convenience (and possibly yours), I put `ggtext_size` function in the [WJSmisc package](https://wjschne.github.io/WJSmisc/).

For more on ggplot font size matters, I found [this post](https://www.christophenicault.com/post/understand_size_dimension_ggplot2/) by Christophe Nicault to be informative.