---
title: Concatenating vectors unless a vector is empty
author: W. Joel Schneider
date: '2021-05-13'
slug: concatenating-vectors-unless-a-vector-is-empty
categories: []
summary: <pre>paste0(empty_vector, non_empty_vector, recycle0 = TRUE)</pre> returns an empty vector.
tags:
  - R
---

```{r setup, include=FALSE}
library(tidyverse)
```

I often need to add a prefix or suffix to a character vector:

```{r}
library(tidyverse)
x <- c("A", "B", "C")
paste0(x, "_1")
```

However, if the vector is empty, I do not want bare prefixes or suffixes like this:

```{r}
x <- character(0)
paste0(x, "_1")
```

I used to write a lot of tedious `if` statements like this:

```{r}
if (length(x) == 0) {
  y <- character(0)
} else {
  y <- paste0(x, "_1")
}
```

For R 4.0.1 and later versions, the `paste` and `paste0` functions acquired the `recycle0` argument. Setting `recycle0` to `TRUE` returns an empty vector if at least one string is empty:

```{r}
paste0(x, "_1", recycle0 = TRUE)
```

If you need to work with an earlier version of R, you can use the `sprintf` function instead:

```{r}
# Non-empty vector
x <- c("A", "B", "C")
sprintf("%s_1", x)

# Empty vector
x <- character(0)
sprintf("%s_1", x)
```

The `glue` function from the glue package also works nicely:

```{r}
# Non-empty vector
x <- c("A", "B", "C")
glue::glue("{x}_1")

# Empty vector
x <- character(0)
glue::glue("{x}_1")
```

